---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: 
  - paperwidth=8.5in
  - paperheight=11in
  - margin=0.05in 
 
header-includes:
  \usepackage{fontspec}
  \setmainfont{Arial}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{/Users/garrettkemp/Documents/Mercer Baseball/Photos for Graphics/Sailor-Bear}}
---

```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(scales)
library(pandoc)
library(ggrepel)
library(ggplot2)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=2cm, height=2cm]{SailorBearOG}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\begin{center}
\textbf{\fontsize{20}{20}\selectfont Arm Care Report:`r params$pitcher`}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=3cm, height=2cm]{SoConLogo}
\end{minipage}

\vspace{-4mm} 
\begin{center}
\textbf{\normalsize `r params$date` vs `r params$opponent`}
\end{center}


\begin{center}
\textbf{\normalsize Game Stats}
\end{center}
\vspace{-2mm} 

```{r game stats, echo=FALSE, warning=FALSE }


kable(game_stats, format = "latex",  linesep = "", align = 'c') %>%
  kable_styling(latex_options = "HOLD_position", position = "center")%>%
  column_spec(1, bold = TRUE, border_left = TRUE) %>%
  row_spec(row = 0, color = "white", background = "#f76800") %>%
  column_spec(ncol(game_stats), border_right = TRUE)
```

\vspace{-4mm} 
\begin{center}
\textbf{\normalsize Pitch Metrics}
\end{center}
\vspace{-2mm} 

```{r pitch metrics,warning=FALSE,echo=FALSE}

pitch_metrics  %>%
  kable(format = "latex",  linesep = "", label = "Game Summary", align = 'c') %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>%
  column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = case_when(
                pitch_metrics$Pitch == "FB" ~ '#d22d49',
                pitch_metrics$Pitch == "2SFB" ~ '#93afd4',
                pitch_metrics$Pitch == "SI" ~ '#de6a04',
                pitch_metrics$Pitch == "SP" ~ '#ddb33a',
                pitch_metrics$Pitch == "CT" ~ '#933f2c',
                pitch_metrics$Pitch == "CH" ~ '#1dbe3a',
                pitch_metrics$Pitch == "SL" ~ '#c3bd0e',
                pitch_metrics$Pitch == "CB" ~ '#00d1ed',
                pitch_metrics$Pitch == "KC" ~ '#854cb5',
                TRUE ~ 'black'
              )
  ) %>% 
  row_spec(row = 0, color = "white", background = "#f76800") %>%
  column_spec(ncol(pitch_metrics), border_right = TRUE) 
```

\vspace{-4mm}
\begin{center}
\textbf{\normalsize Pitch Stats}
\end{center}
\vspace{-2mm} 

```{r pitch stats,warning=FALSE,echo=FALSE}

pitch_stats  %>%
  kable(format = "latex",  linesep = "", label = "Pitch Stats", align = 'c') %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>%
  column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = case_when(
                pitch_stats$Pitch == "FB" ~ '#d22d49',
                pitch_stats$Pitch == "2SFB" ~ '#93afd4',
                pitch_stats$Pitch == "SI" ~ '#de6a04',
                pitch_stats$Pitch == "SP" ~ '#ddb33a',
                pitch_stats$Pitch == "CT" ~ '#933f2c',
                pitch_stats$Pitch == "CH" ~ '#1dbe3a',
                pitch_stats$Pitch == "SL" ~ '#c3bd0e',
                pitch_stats$Pitch == "CB" ~ '#00d1ed',
                pitch_stats$Pitch == "KC" ~ '#854cb5',
                TRUE ~ 'black'
              )
  ) %>% 
  row_spec(row = 0, color = "white", background = "#f76800") %>%
  column_spec(ncol(pitch_stats), border_right = TRUE) 
```


```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 3.4, fig.align='center'} 
# pitch_movement_plot
# arm_angle_plot

gridExtra::grid.arrange(pitch_movement_plot, pitch_release_plot, ncol = 2)
```

\vspace{-1mm} 

```{r echo=FALSE, fig.align='center', fig.height=2.9, fig.width=7.8, message=FALSE, warning=FALSE}

gridExtra::grid.arrange(pitch_velo_plot, pitch_dist_plot, ncol = 2)

```
\vspace{-1mm} 
\newpage

\vspace{-2mm} 

\begin{center}
\begin{minipage}[t]{0.4\textwidth}
\centering
\textbf{\normalsize Pitch Usage vs Left}
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\centering
\textbf{\normalsize Pitch Usage vs Right}
\end{minipage}
\end{center}
\vspace{-3mm} 

```{r Vs R & L, echo=FALSE, message=FALSE, warning=FALSE}

knitr::kables(
  list(
    if(nrow(usage_l) >0){
      knitr::kable(usage_l, valign = 't', align = 'c') %>%
        column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = case_when(
                usage_l$Pitch == "FB" ~ '#d22d49',
                usage_l$Pitch == "2SFB" ~ '#93afd4',
                usage_l$Pitch == "SI" ~ '#de6a04',
                usage_l$Pitch == "SP" ~ '#ddb33a',
                usage_l$Pitch == "CT" ~ '#933f2c',
                usage_l$Pitch == "CH" ~ '#1dbe3a',
                usage_l$Pitch == "SL" ~ '#c3bd0e',
                usage_l$Pitch == "CB" ~ '#00d1ed',
                usage_l$Pitch == "KC" ~ '#854cb5',
                TRUE ~ 'black'
              )
  ) %>% 
        row_spec(row = 0, color = "white", background = "#f76800")%>%
        column_spec(ncol(usage_r), border_right = TRUE)},
    
    if(nrow(usage_r) >0){
      knitr::kable(usage_r,  valign = 't', align = 'c') %>%
        column_spec(1, bold = TRUE, border_left = TRUE, color = "white", 
              background = case_when(
                usage_r$Pitch == "FB" ~ '#d22d49',
                usage_r$Pitch == "2SFB" ~ '#93afd4',
                usage_r$Pitch == "SI" ~ '#de6a04',
                usage_r$Pitch == "SP" ~ '#ddb33a',
                usage_r$Pitch == "CT" ~ '#933f2c',
                usage_r$Pitch == "CH" ~ '#1dbe3a',
                usage_r$Pitch == "SL" ~ '#c3bd0e',
                usage_r$Pitch == "CB" ~ '#00d1ed',
                usage_r$Pitch == "KC" ~ '#854cb5',
                TRUE ~ 'black'
              )
  ) %>% 
        row_spec(row = 0, color = "white", background = "#f76800") %>%
        column_spec(ncol(usage_l), border_right = TRUE) }
  ), 
  format = "latex" )  %>%
  kable_styling(latex_options = "HOLD_position")

```

\vspace{0mm}

```{r Pitch Location, echo=FALSE, warning=FALSE, fig.width=8.4,fig.height=3.25, position= 'center'} 
gridExtra::grid.arrange(plp_lhh, plp_rhh, ncol = 2)
```
\vspace{-1mm} 

\begin{center}
\textbf{\normalsize Situational Pitch Breakdown}
\end{center}
\vspace{0mm} 
```{r breakdown, echo = F, warning = F, position='center', fig.height=3, fig.width=8, fig.align = 'center'}
breakdown
```
